---
title: "Trauma-informed messages"
output: 
  flexdashboard::flex_dashboard:
    theme: journal
    source_code: embed
    storyboard: true
    orientation: rows
    vertical_layout: fill

---

<style>
    .navbar {
      margin: 0;
      padding: 0;
      height: 5%;
      display: block;
      position: fixed
    }
    </style>


```{r setup, include=FALSE}
##issue what does that mean by showing history using flexdashboard function and how can I faciliate you by letting you know which plot to grade.
library(flexdashboard)
library(shiny)
library(gganimate)
library(dygraphs)
library(tidyverse)
library(dplyr)
library(stargazer)
library(interactions)
library(expss)
library(extrafont)
library(cowplot)
library(gganimate)
library(transformr)
library(colorspace)
library(socviz)
library(GGally)
library(Hmisc)
library(lavaan)
library(tidygraph)
library(ggraph)
library(semPlot)
library(knitr)
library(ggridges)
library(cowplot)



```


Research Background
=================

In response to a high prevalence of childhood trauma, which impacts approximately 61% of American adults [CDC, 2021](https://www.cdc.gov/violenceprevention/aces/fastfact.html), and domestic violence, which affects more than one-fourth of American women [NCADV, 2021](https://ncadv.org/STATISTICS), the current randomized controlled trial examines the effects of trauma-informed messages (TIM) on attitudes towards domestic violence. Psychological trauma and domestic violence are often related to psychosocial traits, such as borderline personality disorder symptoms, adverse childhood experiences (ACE), attachment styles towards a parental figure, information processing patterns (i.e., need for cognition (NFC) and faith intuition(FI)), and fear of an intimate partner. Those variables were examined as potential moderators to identify vulnerable female groups. Assessed attitudinal outcomes include trauma knowledge, domestic violence self-efficacy, perceived internal resources to terminate an intimate abusive relationship, perceived tradeoffs, perceived social support, self-efficacy, and an intention to end the relationship. The project features data visualization to provide a holistic understanding of TIM efficacy and effectiveness.

**Participants**

Participants are female MTurk workers (n = 289) self-reporting at least one of the six fear aspects of a current intimate partner on the Fear scale (SAMSHA, 2019) and at least one-adverse childhood experience on the ACE scale (CDC, 2021).

**Method**

Participants were randomly assigned to a) treatment condition (reading a trauma-informed narrative about domestic violence) or b) control condition (reading a classic story about domestic violence). Narratives in both experimental groups feature a fictional female character’s experiences with her abusive partner and a safety plan. A first-person narrative (i.e., using the pronoun “I”) was employed across the two experimental conditions to avoid demographic biases. The trauma-informed condition features psychoeducation regarding the effects of trauma on cognition, emotion, behaviors, and empowerment. Before the randomization process, participants answered questions regarding their psychosocial traits. Once participants read the narrative in their condition, they were asked to answer domestic violence attitudes questions.

**Statistical analysis**

Two- and three-way interactions between experimental conditions (IV), social information processing patterns (Moderator 1), and psychosocial traits (Moderator 2) were explored using R packages. The analysis and visualization codes are embedded (please see Source Code in the navigation bar for the detail).

For more information regarding research background, method, and measurement, please email karikarn@uoregon.edu.


Tables and results
======

column {.sidebar .tabset data-width=650}
---------------------
### Results

This section features the results of two-ways and three-ways interaction between conditions, psychosocial traits, and information processing patterns: the need for cognition (NFC) and faith intuition (FI). Only significant interaction models are featured in the tables.  


### Three-ways interaction 

Condition x NFC x psychosocial traits


### Table1 

Avoidance towards a mother figure


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)
```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)


```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)

```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)


```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+NFC+Mom_avoidance+Condition*Mom_avoidance+Mom_avoidance*NFC+Condition*NFC+Condition*NFC*Mom_avoidance, data)


```



```{r, echo = FALSE, results = 'asis'}

#issue how to get aterisk at the pvalues and how to make the bold goes away
stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 1. F and t-statistics of rational thinking and avoidance attachment to a mother figure as the moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "NFC",
                               "Avoidance",
                          "ConditionxAvoidance", 
                               "NFCxAvoidance",
                          "ConditionxNFC",
                           "ConditionxNFCxAvoidance"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table1"
          )
```

### Table2 

Anxiety towards a mother figure


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+NFC+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*NFC+Condition*NFC+Condition*NFC*Mom_anxiety, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+NFC+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*NFC+Condition*NFC+Condition*NFC*Mom_anxiety, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+NFC+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*NFC+Condition*NFC+Condition*NFC*Mom_anxiety, data)
```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+NFC+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*NFC+Condition*NFC+Condition*NFC*Mom_anxiety, data)


```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+NFC+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*NFC+Condition*NFC+Condition*NFC*Mom_anxiety, data)

```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+NFC+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*NFC+Condition*NFC+Condition*NFC*Mom_anxiety, data)


```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+NFC+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*NFC+Condition*NFC+Condition*NFC*Mom_anxiety, data)


```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 2. F and t-statistics of rational thinking and anxiety attachment to a mother figure as moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "NFC",
                               "Anxiety",
                          "ConditionxAnxiety", 
                               "NFCxAnxiety",
                          "ConditionxNFC",
                           "ConditionxNFCxAnxiety"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table2"
          )
```


### Table 3 

Avoidance towards a father figure

```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+NFC+Dad_avoidance+Condition*Dad_avoidance+Dad_avoidance*NFC+Condition*NFC+Condition*NFC*Dad_avoidance, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+NFC+Dad_avoidance+Condition*Dad_avoidance+Dad_avoidance*NFC+Condition*NFC+Condition*NFC*Dad_avoidance, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+NFC+Dad_avoidance+Condition*Dad_avoidance+Dad_avoidance*NFC+Condition*NFC+Condition*NFC*Dad_avoidance, data)
```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+NFC+Dad_avoidance+Condition*Dad_avoidance+Dad_avoidance*NFC+Condition*NFC+Condition*NFC*Dad_avoidance, data)


```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+NFC+Dad_avoidance+Condition*Dad_avoidance+Dad_avoidance*NFC+Condition*NFC+Condition*NFC*Dad_avoidance, data)

```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+NFC+Dad_avoidance+Condition*Dad_avoidance+Dad_avoidance*NFC+Condition*NFC+Condition*NFC*Dad_avoidance, data)


```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+NFC+Dad_avoidance+Condition*Dad_avoidance+Dad_avoidance*NFC+Condition*NFC+Condition*NFC*Dad_avoidance, data)


```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 3. F and t-statistics of rational thinking and avoidance attachment to a father figure as moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "NFC",
                               "Avoidance",
                          "ConditionxAvoidance", 
                               "NFCxAvoidance",
                          "ConditionxNFC",
                           "ConditionxNFCxAvoidance"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table3"
          )
```

### Table 4 

Anxiety towards a father figure


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+NFC+Dad_anxiety+Condition*Dad_anxiety+Dad_anxiety*NFC+Condition*NFC+Condition*NFC*Dad_anxiety, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+NFC+Dad_anxiety+Condition*Dad_anxiety+Dad_anxiety*NFC+Condition*NFC+Condition*NFC*Dad_anxiety, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+NFC+Dad_anxiety+Condition*Dad_anxiety+Dad_anxiety*NFC+Condition*NFC+Condition*NFC*Dad_anxiety, data)
```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+NFC+Dad_anxiety+Condition*Dad_anxiety+Dad_anxiety*NFC+Condition*NFC+Condition*NFC*Dad_anxiety, data)


```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+NFC+Dad_anxiety+Condition*Dad_anxiety+Dad_anxiety*NFC+Condition*NFC+Condition*NFC*Dad_anxiety, data)

```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+NFC+Dad_anxiety+Condition*Dad_anxiety+Dad_anxiety*NFC+Condition*NFC+Condition*NFC*Dad_anxiety, data)


```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+NFC+Dad_anxiety+Condition*Dad_anxiety+Dad_anxiety*NFC+Condition*NFC+Condition*NFC*Dad_anxiety, data)

```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 4. F and t-statistics of rational thinking and anxiety attachment to a father figure as moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "NFC",
                               "Anxieyu",
                          "ConditionxAnxiety", 
                               "NFCxAnxiety",
                          "ConditionxNFC",
                           "ConditionxNFCxAnxiety"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table4"
          )
```

### Three-ways interaction 

Condition x FI x psychosocial traits


### Table 5 

Adverse childhood experience (ACE)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+FI+ACE+Condition*ACE+ACE*FI+Condition*FI+Condition*FI*ACE, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+FI+ACE+Condition*ACE+ACE*FI+Condition*FI+Condition*FI*ACE, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+FI+ACE+Condition*ACE+ACE*FI+Condition*FI+Condition*FI*ACE, data)
```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+FI+ACE+Condition*ACE+ACE*FI+Condition*FI+Condition*FI*ACE, data)


```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+FI+ACE+Condition*ACE+ACE*FI+Condition*FI+Condition*FI*ACE, data)

```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+FI+ACE+Condition*ACE+ACE*FI+Condition*FI+Condition*FI*ACE, data)


```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+FI+ACE+Condition*ACE+ACE*FI+Condition*FI+Condition*FI*ACE, data)

```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 5. F and t-statistics of emotional thinking and adverse childhood experiences as moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "FI",
                               "ACE",
                          "ConditionxACE", 
                               "FIxACE",
                          "ConditionxFI",
                           "ConditionxFIxACE"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table5"
          )
```


### Table 6 

Fear of an inimate partner


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+FI+Fear+Condition*Fear+Fear*FI+Condition*FI+Condition*FI*Fear, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+FI+Fear+Condition*Fear+Fear*FI+Condition*FI+Condition*FI*Fear, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+FI+Fear+Condition*Fear+Fear*FI+Condition*FI+Condition*FI*Fear, data)
```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+FI+Fear+Condition*Fear+Fear*FI+Condition*FI+Condition*FI*Fear, data)


```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+FI+Fear+Condition*Fear+Fear*FI+Condition*FI+Condition*FI*Fear, data)

```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+FI+Fear+Condition*Fear+Fear*FI+Condition*FI+Condition*FI*Fear, data)


```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+FI+Fear+Condition*Fear+Fear*FI+Condition*FI+Condition*FI*Fear, data)

```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 6. F and t-statistics of emotional thinking and fear of an intimate partner as moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "FI",
                               "Fear",
                          "ConditionxFear", 
                               "FIxFear",
                          "ConditionxFI",
                           "ConditionxFIxFear"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table6"
          )
```


### Table 7 

Anxiety towards a mother figure


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+FI+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*FI+Condition*FI+Condition*FI*Mom_anxiety, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+FI+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*FI+Condition*FI+Condition*FI*Mom_anxiety, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+FI+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*FI+Condition*FI+Condition*FI*Mom_anxiety, data)
```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+FI+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*FI+Condition*FI+Condition*FI*Mom_anxiety, data)


```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+FI+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*FI+Condition*FI+Condition*FI*Mom_anxiety, data)

```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+FI+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*FI+Condition*FI+Condition*FI*Mom_anxiety, data)


```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+FI+Mom_anxiety+Condition*Mom_anxiety+Mom_anxiety*FI+Condition*FI+Condition*FI*Mom_anxiety, data)

```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 7. F and t-statistics of emotional thinking and anxiety attachment towards a mother figure as moderators.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "FI",
                               "Anxiety",
                          "ConditionxAnxiety", 
                               "FIxAnxiety",
                          "ConditionxFI",
                           "ConditionxFIxAnxiety"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table7"
          )
```


### Two-ways interaction 

Conditions x psychosocial traits


### Table 8 

ACE


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+ACE+Condition*ACE, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+ACE+Condition*ACE, data)

```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+ACE+Condition*ACE, data)

```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+ACE+Condition*ACE, data)



```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+ACE+Condition*ACE, data)


```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+ACE+Condition*ACE, data)



```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+ACE+Condition*ACE, data)


```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 8. F and t-statistics of  adverse childhood experience as the moderator.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "ACE",
                               "ConditionxACE"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table8"
          )
```


### Table 9 

Fear of a current intimate partner


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+Fear+Condition*Fear, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+Fear+Condition*Fear, data)

```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+Fear+Condition*Fear, data)

```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+Fear+Condition*Fear, data)



```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+Fear+Condition*Fear, data)


```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+Fear+Condition*Fear, data)



```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+Fear+Condition*Fear, data)


```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 9. F and t-statistics of  fear of a current intimate partner as the moderator.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "Fear",
                               "ConditionxFear"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table9"
          )
```


### Table 10 

Borderline personality traits (BPD)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+BPD+Condition*BPD, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+BPD+Condition*BPD, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+BPD+Condition*BPD, data)

```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+BPD+Condition*BPD, data)



```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+BPD+Condition*BPD, data)


```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+BPD+Condition*BPD, data)



```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+BPD+Condition*BPD, data)


```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 10. F and t-statistics of borderline personality traits as the moderator.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "BPD",
                               "ConditionxBPD"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table10"
          )
```


### Table 11 

Anxious attachment towards a mother figure


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+Mom_anxiety+Condition*Mom_anxiety, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+Mom_anxiety+Condition*Mom_anxiety, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+Mom_anxiety+Condition*Mom_anxiety, data)

```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+Mom_anxiety+Condition*Mom_anxiety, data)



```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+Mom_anxiety+Condition*Mom_anxiety, data)


```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+Mom_anxiety+Condition*Mom_anxiety, data)



```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+Mom_anxiety+Condition*Mom_anxiety, data)


```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 11. F and t-statistics of anxiety towards a mother figure as the moderator.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "Anxiety",
                               "ConditionxAnxiety"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table11"
          )
```

### Table 12 

Anxious attachment towards a father figure


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```

```{r, echo = FALSE}
#Create models according to DVs
model1Mavo<-lm(Trauma_Knowledge~Condition+Dad_anxiety+Condition*Dad_anxiety, data)

```


```{r, echo = FALSE}
model2Mavo<-lm(DVS_state~Condition+Dad_anxiety+Condition*Dad_anxiety, data)
```


```{r, echo = FALSE}
model3Mavo<-lm(Empowerment_InternalTools~Condition+Dad_anxiety+Condition*Dad_anxiety, data)

```


```{r, echo = FALSE}
model4Mavo<-lm(Empowerment_Tradeoffs~Condition+Dad_anxiety+Condition*Dad_anxiety, data)


```


```{r, echo = FALSE}
model5Mavo<-lm(Empowerment_ExpectationSupport~Condition+Dad_anxiety+Condition*Dad_anxiety, data)

```


```{r, echo = FALSE}
model6Mavo<-lm(SelfCompassion~Condition+Dad_anxiety+Condition*Dad_anxiety, data)



```


```{r, echo = FALSE}
model7Mavo<-lm(In_End~Condition+Dad_anxiety+Condition*Dad_anxiety, data)


```



```{r, echo = FALSE, results = 'asis'}

stargazer(model1Mavo, model2Mavo, model3Mavo, model4Mavo, model5Mavo, model6Mavo, model7Mavo,
          
          title =  "Table 12. F and t-statistics of anxiety towards a father figure as the moderator.",
          df =F,
          dep.var.labels =c("Trauma knowledge", "Self-efficacy", "Internal tools", "Tradeoffs", "Social support", "Self-compassion", "Leaving intention"),
          covariate.labels = c("Constant",
                               "Condition", 
                               "Anxiety",
                               "ConditionxAnxiety"),
        
          
          type = "html", 
          align = TRUE, 
  
         
    
          intercept.bottom = F,
          intercept.top = T,
          digits = 2,
          single.row = T, out="Table12"
          )
```




Row {.tabset data-height=500}
---------------------


Below are uncertainty plots of significant results from the interaction tables. Uncertainty A(B) represents uncertainty from Table A column B. 

### Uncertainty 1(7)


```{r}

data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Intention<-data$In_End
data$Avoidance<-data$Mom_avoidance

```

```{r}
model7Mavo<-lm(Intention~Condition+NFC+Avoidance+Condition*Avoidance+Avoidance*NFC+Condition*NFC+Condition*NFC*Avoidance, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"), legend.position = "bottom")+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```



### Uncertainty 2(7)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Intention<-data$In_End
data$Anxiety<-data$Mom_anxiety

```

```{r}
model7Mavo<-lm(Intention~Condition+NFC+Anxiety+Condition*Anxiety+Anxiety*NFC+Condition*NFC+Condition*NFC*Anxiety, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r,eval=FALSE}

#Another version (not to be used here)

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.8) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 1.2) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 1.6)


```


```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```



```{r, eval = FALSE}
# This is another version not used here
p<-p+ scale_color_manual("Confidence Interval", 
                      values = c("#56a926",
                                 lighten("#56a926", .3),
                                 lighten("#56a926", .6)))+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
```


### Uncertainty 3(2)

```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Efficacy<-data$DVS_state
data$Avoidance<-data$Dad_avoidance

```

```{r}
model7Mavo<-lm(Efficacy~Condition+NFC+Avoidance+Condition*Avoidance+Avoidance*NFC+Condition*NFC+Condition*NFC*Avoidance, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```



```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```


### Uncertainty 3(3)

```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Tools<-data$Empowerment_InternalTools
data$Avoidance<-data$Dad_avoidance

```

```{r}
model7Mavo<-lm(Tools~Condition+NFC+Avoidance+Condition*Avoidance+Avoidance*NFC+Condition*NFC+Condition*NFC*Avoidance, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```

### Uncertainty 3(5)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Support<-data$Empowerment_ExpectationSupport
data$Avoidance<-data$Dad_avoidance

```

```{r}
model7Mavo<-lm(Support~Condition+NFC+Avoidance+Condition*Avoidance+Avoidance*NFC+Condition*NFC+Condition*NFC*Avoidance, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```

### Uncertainty 3(6)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Compassion<-data$SelfCompassion
data$Avoidance<-data$Dad_avoidance

```

```{r}
model7Mavo<-lm(Compassion~Condition+NFC+Avoidance+Condition*Avoidance+Avoidance*NFC+Condition*NFC+Condition*NFC*Avoidance, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```

### Uncertainty 4(5)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Support<-data$Empowerment_ExpectationSupport
data$Anxiety<-data$Dad_anxiety

```

```{r}
model7Mavo<-lm(Support~Condition+NFC+Anxiety+Condition*Anxiety+Anxiety*NFC+Condition*NFC+Condition*NFC*Anxiety, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```

### Uncertainty 5(3)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Tools<-data$Empowerment_InternalTools


```

```{r}
model7Mavo<-lm(Tools~Condition+FI+ACE+Condition*ACE+ACE*FI+Condition*FI+Condition*FI*ACE, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```

### Uncertainty 5(5)



```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Intention<-data$In_End
data$Avoidance<-data$Mom_avoidance

```

```{r}
model7Mavo<-lm(Intention~Condition+NFC+Avoidance+Condition*Avoidance+Avoidance*NFC+Condition*NFC+Condition*NFC*Avoidance, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```

### Uncertainty 6(4)



```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Support<-data$Empowerment_ExpectationSupport


```

```{r}
model7Mavo<-lm(Support~Condition+FI+Fear+Condition*Fear+Fear*FI+Condition*FI+Condition*FI*Fear, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```


### Uncertainty 7(1)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Knowledge<-data$Trauma_Knowledge
data$Anxiety<-data$Mom_anxiety

```

```{r}
model7Mavo<-lm(Knowledge~Condition+FI+Anxiety+Condition*Anxiety+Anxiety*FI+Condition*FI+Condition*FI*Anxiety, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```


### Uncertainty 7(2)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Efficacy<-data$DVS_state
data$Anxiety<-data$Mom_anxiety

```

```{r}
model7Mavo<-lm(Efficacy~Condition+FI+Anxiety+Condition*Anxiety+Anxiety*FI+Condition*FI+Condition*FI*Anxiety, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```


### Uncertainty 8


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Knowledge<-data$Trauma_Knowledge


```

```{r}
model7Mavo<-lm(Knowledge~Condition+ACE+Condition*ACE, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```

### Uncertainty 9(1)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Knowledge<-data$Trauma_Knowledge


```

```{r}
model7Mavo<-lm(Knowledge~Condition+Fear+Condition*Fear, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```

### Uncertainty 10(1)

```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Knowledge<-data$Trauma_Knowledge


```

```{r}
model7Mavo<-lm(Knowledge~Condition+BPD+Condition*BPD, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```


### Uncertainty 11(1)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Knowledge<-data$Trauma_Knowledge
data$Anxiety<-data$Mom_anxiety


```

```{r}
model7Mavo<-lm(Knowledge~Condition+Anxiety+Condition*Anxiety, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```




### Uncertainty 11(3)



```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Tools<-data$Empowerment_InternalTools
data$Anxiety<-data$Mom_anxiety

```

```{r}
model7Mavo<-lm(Tools~Condition+Anxiety+Condition*Anxiety, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```


### Uncertainty 12(1)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Knowledge<-data$Trauma_Knowledge
data$Anxiety<-data$Dad_anxiety


```

```{r}
model7Mavo<-lm(Knowledge~Condition+Anxiety+Condition*Anxiety, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```



```{r}
un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"))+
  labs(title = "Standard errors of the model in Plot 1 \n across 80% CI, 90% CI, and 95%CI", x = "Estimates", y = "Predictors")
  
```

```{r}
p
```


Row {.tabset data-height=500}
---------------------

Below are Johnson-Neyman (JN) plots of significant results from the interaction tables. Figure A(B) represents JN results of the interaction from Table A column B. 


### Figure 1(7)


```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_avoidance", "NFC", "Condition", "In_End")

```


```{r}
model7MavoJN<-lm(In_End~Condition*NFC*Mom_avoidance, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "NFC", mod2 = "Mom_avoidance", jnplot = TRUE, 
           mod2.labels = c("Mean of avoidance - SD", "Mean of avoidance", "Mean of avoidance + 1 SD"),
  
                
x.label = "Rational thinking pattern",
main.title = "3-ways interaction:condition, rational thinking, avoidance attachment")
 

 
           
           
        
           
```

### Figure 2(7)


```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_anxiety", "NFC", "Condition", "In_End")

```


```{r}
model7MavoJN<-lm(In_End~Condition*NFC*Mom_anxiety, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "NFC", mod2 = "Mom_anxiety", jnplot = TRUE, 
           mod2.labels = c("Mean of anxiety - SD", "Mean of anxiety", "Mean of anxiety + 1 SD"),
  
                
x.label = "Rational thinking pattern",
main.title = "3-ways interaction:condition, rational thinking, anxiety attachment")
 

 
           
           
        
           
```

### Figure 3(2)


```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Dad_avoidance", "NFC", "Condition", "DVS_state")

```


```{r}
model7MavoJN<-lm(DVS_state~Condition*NFC*Dad_avoidance, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "NFC", mod2 = "Dad_avoidance", jnplot = TRUE, 
           mod2.labels = c("Mean of avoidance - SD", "Mean of avoidance", "Mean of avoidance + 1 SD"),
  
                
x.label = "Rational thinking pattern",
main.title = "3-ways interaction:condition, rational thinking, avoidance attachment")
 

 
           
           
        
           
```

### Figure 3(3)


```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Dad_avoidance", "NFC", "Condition", "Empowerment_InternalTools")

```


```{r}
model7MavoJN<-lm(Empowerment_InternalTools~Condition*NFC*Dad_avoidance, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "NFC", mod2 = "Dad_avoidance", jnplot = TRUE, 
           mod2.labels = c("Mean of avoidance - SD", "Mean of avoidance", "Mean of avoidance + 1 SD"),
  
                
x.label = "Rational thinking pattern",
main.title = "3-ways interaction:condition, rational thinking, avoidance attachment")
 

 
           
           
        
           
```


### Figure 3(5)


```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Dad_avoidance", "NFC", "Condition", "Empowerment_ExpectationSupport")

```


```{r}
model7MavoJN<-lm(Empowerment_ExpectationSupport~Condition*NFC*Dad_avoidance, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "NFC", mod2 = "Dad_avoidance", jnplot = TRUE, 
           mod2.labels = c("Mean of avoidance - SD", "Mean of avoidance", "Mean of avoidance + 1 SD"),
  
                
x.label = "Rational thinking pattern",
main.title = "3-ways interaction:condition, rational thinking, avoidance attachment")
 

 
           
           
        
           
```


### Figure 3(6)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Dad_avoidance", "NFC", "Condition", "SelfCompassion")

```


```{r}
model7MavoJN<-lm(SelfCompassion~Condition*NFC*Dad_avoidance, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "NFC", mod2 = "Dad_avoidance", jnplot = TRUE, 
           mod2.labels = c("Mean of avoidance - SD", "Mean of avoidance", "Mean of avoidance + 1 SD"),
  
                
x.label = "Rational thinking pattern",
main.title = "3-ways interaction:condition, rational thinking, avoidance attachment")
 

 
           
           
        
           
```

### Figure 4(5)


```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Dad_anxiety", "NFC", "Condition", "Empowerment_ExpectationSupport")

```


```{r}
model7MavoJN<-lm(Empowerment_ExpectationSupport~Condition*NFC*Dad_anxiety, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "NFC", mod2 = "Dad_anxiety", jnplot = TRUE, 
           mod2.labels = c("Mean of anxiety - SD", "Mean of anxiety", "Mean of anxiety + 1 SD"),
  
                
x.label = "Rational thinking pattern",
main.title = "3-ways interaction:condition, rational thinking, anxiety attachment")
 

 
           
           
        
           
```


### Figure 5(3)


```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("ACE", "FI", "Condition", "Empowerment_InternalTools")

```


```{r}
model7MavoJN<-lm(Empowerment_InternalTools~Condition*FI*ACE, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "FI", mod2 = "ACE", jnplot = TRUE, 
           mod2.labels = c("Mean of ACE - SD", "Mean of ACE", "Mean of ACE + 1 SD"),
  
                
x.label = "Emotional thinking pattern",
main.title = "3-ways interaction:condition, emotional thinking, ACE")
 

 
           
           
        
           
```


### Figure 5(5)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("ACE", "FI", "Condition", "Empowerment_ExpectationSupport")

```


```{r}
model7MavoJN<-lm(Empowerment_ExpectationSupport~Condition*FI*ACE, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "FI", mod2 = "ACE", jnplot = TRUE, 
           mod2.labels = c("Mean of ACE - SD", "Mean of ACE", "Mean of ACE + 1 SD"),
  
                
x.label = "Emotional thinking pattern",
main.title = "3-ways interaction:condition, emotional thinking, ACE")
 

 
           
           
        
           
```


### Figure 6(5)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Fear", "FI", "Condition", "Empowerment_ExpectationSupport")

```


```{r}
model7MavoJN<-lm(Empowerment_ExpectationSupport~Condition*FI*Fear, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "FI", mod2 = "Fear", jnplot = TRUE, 
           mod2.labels = c("Mean of fear - SD", "Mean of fear", "Mean of fear + 1 SD"),
  
                
x.label = "Emotional thinking pattern",
main.title = "3-ways interaction:condition, emotional thinking, fear")
 

 
           
           
        
           
```


### Figure 7(1)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_anxiety", "FI", "Condition", "Trauma_Knowledge")

```


```{r}
model7MavoJN<-lm(Trauma_Knowledge~Condition*FI*Mom_anxiety, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "FI", mod2 = "Mom_anxiety", jnplot = TRUE, 
           mod2.labels = c("Mean of anxiety - SD", "Mean of anxiety", "Mean of anxiety + 1 SD"),
  
                
x.label = "Emotional thinking pattern",
main.title = "3-ways interaction:condition, emotional thinking, anxiety")
 

 
           
           
        
           
```



### Figure 7(2)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_anxiety", "FI", "Condition", "DVS_state")

```


```{r}
model7MavoJN<-lm(DVS_state~Condition*FI*Mom_anxiety, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "FI", mod2 = "Mom_anxiety", jnplot = TRUE, 
           mod2.labels = c("Mean of anxiety - SD", "Mean of anxiety", "Mean of anxiety + 1 SD"),
  
                
x.label = "Emotional thinking pattern",
main.title = "3-ways interaction:condition, emotional thinking, anxiety")
 

 
           
           
        
           
```


### Figure 7(4)


```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_anxiety", "FI", "Condition", "Empowerment_Tradeoffs")

```


```{r}
model7MavoJN<-lm(Empowerment_Tradeoffs~Condition*FI*Mom_anxiety, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "FI", mod2 = "Mom_anxiety", jnplot = TRUE, 
           mod2.labels = c("Mean of anxiety - SD", "Mean of anxiety", "Mean of anxiety + 1 SD"),
  
                
x.label = "Emotional thinking pattern",
main.title = "3-ways interaction:condition, emotional thinking, anxiety")
 

 
           
           
        
           
```


### Figure 8(1)


```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("ACE", "Condition", "Trauma_Knowledge")

```


```{r}
model7MavoJN<-lm(Trauma_Knowledge~Condition*ACE, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "ACE", jnplot = TRUE, 
           mod2.labels = c("Mean of ACE - SD", "Mean of ACE", "Mean of ACE + 1 SD"),
  
                
x.label = "Adverse childhood experiences",
main.title = "2-ways interaction:condition and ACE")
 

 
           
           
        
           
```

### Figure 9(1)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Fear", "Condition", "Trauma_Knowledge")

```


```{r}
model7MavoJN<-lm(Trauma_Knowledge~Condition*Fear, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "Fear", jnplot = TRUE, 
           mod2.labels = c("Mean of fear - SD", "Mean of fear", "Mean of fear + 1 SD"),
  
                
x.label = "Fear of an intimate partner",
main.title = "2-ways interaction:condition and fear")
 

 
           
           
        
           
```


### Figure 10(1)




```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("BPD", "Condition", "Trauma_Knowledge")

```


```{r}
model7MavoJN<-lm(Trauma_Knowledge~Condition*BPD, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "BPD", jnplot = TRUE, 
           mod2.labels = c("Mean of BPD - SD", "Mean of BPD", "Mean of BPD + 1 SD"),
  
                
x.label = "Borderline personality traits",
main.title = "2-ways interaction:condition and BPD")
 

 
           
           
        
           
```


### Figure 10(7)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("BPD", "Condition", "In_End")

```


```{r}
model7MavoJN<-lm(In_End~Condition*BPD, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "BPD", jnplot = TRUE, 
           mod2.labels = c("Mean of BPD - SD", "Mean of BPD", "Mean of BPD + 1 SD"),
  
                
x.label = "Borderline personality traits",
main.title = "2-ways interaction:condition and BPD")
 

 
           
           
        
           
```

### Figure 11(1)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_anxiety", "Condition", "Trauma_Knowledge")

```


```{r}
model7MavoJN<-lm(Trauma_Knowledge~Condition*Mom_anxiety, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "Mom_anxiety", jnplot = TRUE, 
           mod2.labels = c("Mean of anxiety - SD", "Mean of anxiety", "Mean of anxiety + 1 SD"),
  
                
x.label = "Anxiety attachment scores towads a mother figure",
main.title = "2-ways interaction:condition and anxiety")
 

 
           
           
        
           
```


### Figure 11(3)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_anxiety", "Condition", "Empowerment_InternalTools")

```


```{r}
model7MavoJN<-lm(Empowerment_InternalTools~Condition*Mom_anxiety, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "Mom_anxiety", jnplot = TRUE, 
           mod2.labels = c("Mean of anxiety - SD", "Mean of anxiety", "Mean of anxiety + 1 SD"),
  
                
x.label = "Anxiety attachment scores towads a mother figure",
main.title = "2-ways interaction:condition and anxiety")
 

 
           
           
        
           
```


### Figure 12(1)



```{r}
#issue adjust size of letters 
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Dad_anxiety", "Condition", "Trauma_Knowledge")

```


```{r}
model7MavoJN<-lm(Trauma_Knowledge~Condition*Dad_anxiety, Plot1data)
```



```{r echo = FALSE, results= 'hide', fig.height=10, fig.width=19}
sim_slopes(model7MavoJN, pred = "Condition", modx = "Dad_anxiety", jnplot = TRUE, 
           mod2.labels = c("Mean of anxiety - SD", "Mean of anxiety", "Mean of anxiety + 1 SD"),
  
                
x.label = "Anxiety attachment scores towads a father figure",
main.title = "2-ways interaction:condition and anxiety")
 

 
           
           
        
           
```




Visualization {.storyboard}
=====

### Plot 1(Draft)


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
#Create a new data frame for a correlation plot
data<-data %>% select(Condition, ACE, BPD, Fear, Mom_avoidance,
                      Mom_anxiety, Dad_avoidance, Dad_anxiety, NFC, 
                      FI, DVS_state, Trauma_Knowledge, Empowerment_Tradeoffs,
                      Empowerment_InternalTools, Empowerment_ExpectationSupport, 
                      DVS_state)
```


```{r}
#remove missing cases 
data<-na.omit(data)
```



```{r}
#create a correlation matrix
data_cor<-rcorr(as.matrix(data))
```


```{r, results='hide'}
#create a co-efficient column
data.frame(data_cor$r) %>% head() %>% kable()
```

```{r, results='hide'}
# p values column
data.frame(data_cor$P) %>% head() %>% kable()
```


```{r, results='hide'}
#n column
data.frame(data_cor$n) %>% head() %>% kable()
```


```{r}
cors <- function(df) {
   M <- Hmisc::rcorr(as.matrix(df))
   Mdf <- map(M, ~data.frame(.x))
  }
```


```{r, results='hide'}
cors(data) %>% first() %>% head %>% kable()
```


```{r, results='hide'}
cors(data) %>% 
  map(~rownames_to_column(.x, var = "measure1")) %>% 
  map(~pivot_longer(.x, -measure1, "measure2")) %>% 
  bind_rows(.id = "id") %>% 
  pivot_wider(names_from = id,  values_from = value) %>% 
  rename(p = P) %>% 
  mutate(sig_p = ifelse(p < .05,T, F),
         p_if_sig = ifelse(sig_p, p, NA), 
         r_if_sig = ifelse(sig_p, r, NA)) %>% 
  head() %>% 
  kable()
```


```{r, results='hide'}
#Turned format correlations to a function 
formatted_cors<-function(df){
  cors(df)%>%
    map(~rownames_to_column(.x, var="measure1")) %>%
    map(~pivot_longer(.x, -measure1, "measure2")) %>%
    bind_rows(.id = "id") %>%
    pivot_wider(names_from = id, values_from = value) %>%
    rename(p = P) %>%
    mutate(sig_p = ifelse(p < .05, T, F),
           p_if_sig = ifelse(sig_p, p, NA),
           r_if_sig = ifelse(sig_p, r, NA)) 
}

```


```{r, results = 'hide'}
formatted_cors(data) %>% head() %>% kable()
```


```{r}
#Plotting 
formatted_cors(data) %>% 
  ggplot(aes(x = measure1, y = measure2, fill = r))+
  geom_tile()+
  labs(x = NULL, y = NULL, fill = "Pearson's \n correlations", 
       title = "Correlations of key variables",
       subtitle = "Only significant correlations (*p < .05*) 
       are displayed in numbers")+
  scale_fill_viridis_c()+
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0),
                   labels = c("Condition", "ACE", "BPD", "Fear", "Avoidance(mother)",
                              "Anxiety (mother)", "Avoidance(father)", "Anxiety (father)",
                              "NFC", "FI", "Self-efficacy", "Knowledge", "Self-tools",
                              "Tradeoffs", "Support")) +
  theme(text=element_text(family="Calibri"),
        plot.title = element_text(face = 'bold', hjust = 0.5))
```

---

This plot utilizes geom_tile to create a correlation table of key variables in the current study (please see Research Background in the navigation bar for research context). Although correlation visualization packages, such as [corrplot](https://cran.r-project.org/web/packages/corrplot/corrplot.pdf), are easy to use, ggplot is more flexible in terms of visual customization. A trade-off relative to other correlation visualization packages is that data preparation for a ggplot can be complicated and takes a longer time to be done (see Source Code). The current plot utilizes geom_title to display correlation strengths with lighter colors indicates a higher Pearson's coefficient. [A Viridis color palette](https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html) is used for colorblind friendliness. 

The plot posits specific issues. First, some of the y axis labels overlap and should be adjusted. Second, although the colors might indicate the strength of correlation coefficients for each pair of variables, viewers may better understand if correlation numbers are displayed. To decrease cognitive load, only significant numbers should be displayed. Besides, the plot's legend extends beyond the storyboard and could have been moved to be under the plot.  The plot could have been resized to fit the storyboard better. The mentioned issues will be fixed in the final plot. 

### Plot 1(final)

```{r, fig.height=10, fig.width=15}
#add significant correlations in table 

p<-formatted_cors(data) %>%
  ggplot(aes(measure1, measure2, fill=r, label=round(r_if_sig,2))) +
  geom_tile() +
  labs(x = NULL, y = NULL, fill = "Pearson's\nCorrelation", title="Correlations of key variables",
       subtitle="Only significant Pearson's correlation coefficients shown") +
  scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
  geom_text() +
  theme_classic() +
  scale_x_discrete(expand=c(0,0), labels = c("Condition", "ACE", "BPD", "Fear", "Avoidance(mother)", "Anxiety (mother)", "Avoidance(father)", "Anxiety (father)", "NFC", "FI", "Self-efficacy", "Knowledge", "Self-tools", "Tradeoffs", "Support")) +
  scale_y_discrete(expand=c(0,0), labels = c("Condition", "ACE", "BPD", "Fear", "Avoidance(mother)", "Anxiety (mother)", "Avoidance(father)", "Anxiety (father)", "NFC", "FI", "Self-efficacy", "Knowledge", "Self-tools", "Tradeoffs", "Support")) +
  theme(text=element_text(family="Calibri", size = 15), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, vjust = 0.70))
```

```{r}
p
```


---

The final version of plot 1 addresses the issues stated in the draft. Significant correlation coefficients were filled in the geom_tile. The colors of the plot were adjusted to facilitate viewers' understanding of the direction of correlations. Correlation coefficients that are closed to zero are highlighted in a lighter color. Correlation coefficients ranging from zero to one are highlighted in a red shade with darker colors representing higher correlation coefficients (closer to 1). The blue shade represents correlation coefficients ranging from zero to minus 1, with darker colors represent lower correlation coefficients (closer to -1.)  The x-axis labels were rotated at a 45-degree angle such that they do not overlap. The legend was moved to the bottom of the plot to not extend beyond the storyboard space. 

The results in the plot are consistent with trauma-related theories. For example, women with a higher level of adverse childhood experience (ACE) likely to have more borderline personality disorder (BPD) symptoms and fear towards an intimate abusive partner.  


### Plot 2 draft 

```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Intention<-data$In_End
data$Anxiety<-data$Mom_anxiety

```

```{r}
model7Mavo<-lm(Intention~Condition+NFC+Anxiety+Condition*Anxiety+Anxiety*NFC+Condition*NFC+Condition*NFC*Anxiety, data)


```


```{r}
un_model7Mavo<-broom::tidy(model7Mavo, conf.int = TRUE)

```


```{r}
#adjust the size of the lines

p <- ggplot(un_model7Mavo, aes(term, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.4) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 0.6) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 0.8)

```




```{r}
p
```

----
This plot depicts a draft version of standard errors of a three-way interaction between NFC (i.e., need for cognition), experimental conditions (control versus treatment), and anxiety attachments towards a mother figure. The plot posits some issues. First, estimates are on the y-axis, which might be challenging to interpret. The y-axis tick mark labels are wide in intervals (i.e., four each). Regarding the x-axis, the intercept could have been excluded to decrease viewers' cognitive burden as the parameter is not meaningful for interpretation in the current research context. Some labels, such as "Condition: NFC," which might be challenging to see in the current plot, are also unclear as viewers may not understand whether the term refers to the treatment or control condition. Variables on the x-axis overlap. The legend is also labeled with the word 'color' rather than a meaningful term such as 'confidence interval.' The mentioned issues will be fixed in the final version of the draft. 

### Plot 2(final)

```{r}

un_model7Mavo<-subset(un_model7Mavo, term %nin% "(Intercept)")
un_model7Mavo$nicelabs <-prefix_strip(un_model7Mavo$term, "Condition")

```


```{r,eval=FALSE}

#Another version (not to be used here)

p <- ggplot(un_model7Mavo, aes(nicelabs, estimate))+
    geom_hline(yintercept = 0,
             color = "cornflowerblue",
             linetype = 2) +
  geom_errorbar(aes(ymin = estimate + qnorm(.025)*std.error, 
                    ymax = estimate + qnorm(.975)*std.error,
                    color = "95%"),
                width = 0.2,
                size = 0.8) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.05)*std.error, 
                    ymax = estimate + qnorm(.95)*std.error,
                    color = "90%"),
                width = 0.2,
                size = 1.2) + 
  geom_errorbar(aes(ymin = estimate + qnorm(.1)*std.error, 
                    ymax = estimate + qnorm(.9)*std.error,
                    color = "80%"),
                width = 0.2,
                size = 1.6)


```


```{r}
p<-p+ scale_color_viridis_d("Confidence Interval")+
  geom_point() +
  coord_flip()+
  theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(hjust = 0.5, color = "#5c8761"), legend.position = "bottom")+
  labs(title = "Standard errors of the interaction between conditions, NFC,  \n and anxiety attachment across 80% CI, 90% CI, and 95%CI", x = "Predictors", y = "Estimates")
 
```

```{r}
p
```

---

The final version of Plot2 addresses the issues mentioned in the draft. The estimates were plotted on the x-axis, and the terms are plotted on the y axis with the label 'predictors,' which enables viewers to interpret the plot easily. The grid background was removed, and a minimal theme was introduced to exclude unmeaningful components (e.g., the grid color) and decrease the cognitive load. A colorblind-friendly package (scale_color_viridis_d) was presented to illustrate confidence interval levels. The legend title was changed from  'color' in the draft version to 'confidence interval' in the current plot. The term 'terms' was changed to 'predictors' to facilitate viewers' understanding. The axis tick mark labels of estimates are narrower in intervals (2.5) relative to those of the draft version (4.0). 

Regarding the interpretation, the plot represents standard errors (SE) of the interaction between treatment (exposure to trauma-informed messages), cognitive information processing, and anxiety attachment towards a mother figure. The interaction term's standard errors approximately ranged from 0 - 0.625 at the 95% CI and narrower than the 80% CI range. The treatment's main effect is roughly close to -.7.5 to slightly more than zero at the 95% CI. The SE ranges are narrower at the 80% CI (approximately from -1.25 to close to  -6.25). The standard errors of the treatment's main effect are relatively high, indicating that the treatment's main effect might not be reliable and significant. The interaction effects' standard errors at every confident interval level are relatively low, meaning that the results are significant. See the Tables and Results tab for more detail. 

### Plot 3 draft 


```{r}

data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_avoidance", "NFC", "Condition", "In_End")

```



```{r}
Plot1data<-na.omit(Plot1data)
```


```{r}
 
Plot1data$Mom_avoidance <- cut(Plot1data$Mom_avoidance, breaks=c(1, 1.8, 2.72, 3.63, 5), include.lowest= TRUE)
```




```{r}
Plot1data$Condition <- factor(Plot1data$Condition,
levels = c(0,1),
labels = c("Control" , "Treatment"))
```


```{r}

Plot1data$Mom_avoidance <- factor(Plot1data$Mom_avoidance,
levels = c("[1,1.8]"   ,  "(1.8,2.72]"  ,"(2.72,3.63]" ,"(3.63,5]" ),
labels = c("Less than -1 SD", "-1SD to mean", "Mean to + 1SD", "More than+ 1SD"))




```


```{r}


ggplot(Plot1data, aes(x  = NFC, y = In_End, color = Condition))+
  geom_point(alpha = 0.4, position = "jitter")+
  geom_smooth(method = "lm", se  = FALSE)+
  facet_wrap(~Mom_avoidance, scales = "free")+
  theme_minimal()+
  labs(x =  "Rational thinking", 
       y = "Leaving intention",  
       title = "The interaction effects of conditions, avoidance attachment, and \n thinking pattern on leaving intention", 
       subtitle = "Avoidance attachment scores towards a mother figure")+
  theme(text = element_text(family = "Calibri"), plot.title = element_text(face = "bold", hjust = 0.5, size = 12))
```

 
---

The plot depicts the three-way interaction between conditions and rational thinking across different avoidance attachment levels towards a mother figure. Although the plot is relatively straightforward for interpretation, it posits specific issues. First, avoidance attachment scores are categorized into four groups,  but the significant point of the interaction between condition and rational thinking in each attachment level is unclear. Adding a significant line and a text label might be helpful. Second, the title and subtitle are in the same color. Although the title is bold, some viewers may have difficulty separating the subtitle from the title. The scale colors are not colorblind-friendly, and the legend labels extend beyond the storyboard. Those issues will be fixed in the final draft.


### Plot 3 final 



```{r}

data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_avoidance", "NFC", "Condition", "In_End")

```



```{r}
Plot1data<-na.omit(Plot1data)
```


```{r}
 
Plot1data$Mom_avoidance <- cut(Plot1data$Mom_avoidance, breaks=c(1, 1.8, 2.72, 3.63, 5), include.lowest= TRUE)
```




```{r}
Plot1data$Condition <- factor(Plot1data$Condition,
levels = c(0,1),
labels = c("Control" , "Treatment"))
```


```{r}

Plot1data$Mom_avoidance <- factor(Plot1data$Mom_avoidance,
levels = c("[1,1.8]"   ,  "(1.8,2.72]"  ,"(2.72,3.63]" ,"(3.63,5]" ),
labels = c("Less than -1 SD", "-1SD to mean", "Mean to + 1SD", "More than+ 1SD"))




```


```{r, fig.width=6}
txt_data <- data.frame(
  NFC = rep(3.99, 4),
  In_End = rep(4.5, 4),
  txt = c(rep("Sig", 3), ""),
  Mom_avoidance = levels(Plot1data$Mom_avoidance)
)

ggplot(Plot1data, aes(x  = NFC, y = In_End, color = Condition))+
  geom_point(alpha = 0.4, position = "jitter")+
  geom_smooth(method = "lm", se  = FALSE)+
  facet_wrap(~Mom_avoidance, scales = "free")+
  scale_y_continuous(limits = c(1,5))+
  scale_x_continuous(limits = c(1,5))+
   scale_color_manual(values = c("#E1BE6A", "#40B0A6"))+
  theme_minimal()+
  geom_text(aes(x = NFC, y = In_End, label = txt),
            hjust = 0,
            size = 3.5,
            data = txt_data,
            inherit.aes = FALSE) +
  labs(x =  "Rational thinking", 
       y = "Leaving intention",  
       title = "The interaction effects of conditions, avoidance attachment, and \n thinking pattern on leaving intention",
       subtitle = "Avoidance attachment scores towards a mother figure",
       caption = "Sig indicates the initial point of the significant interation \n between condition and rational thinking for significant avoidance facets")+
  theme(text = element_text(family = "Calibri", size = 10), plot.title = element_text(face = "bold", hjust = 0.5, size = 12, color = "#26734d"), legend.position = "bottom", plot.caption = element_text(hjust = 0))+
   geom_vline(data = filter(Plot1data, Mom_avoidance == "Less than -1 SD"), aes(xintercept = 3.93), color = "black", linetype = "dotted")+
  geom_vline(data = filter(Plot1data, Mom_avoidance == "-1SD to mean"), aes(xintercept = 3.93), color = "black", linetype = "dotted")+
   geom_vline(data = filter(Plot1data, Mom_avoidance == "Mean to + 1SD"), aes(xintercept = 3.93), color = "black", linetype = "dotted")
```

 
----

The final version of plot 3 addresses issues mentioned in the draft. Significant lines were added across three facets of avoidance attachment to represent significant points of the interaction between condition and rational thinking with the 'sig' text labels. The legend was moved to under the plot such that the legend label does not extend the storyline. The colors of the title and subtitle are different for easy categorization. The scale colors were adjusted to be colorblind-friendly. A caption was added to clarify the meaning of the word 'sig' in each significant avoidance facet.  

Regarding the interpretation, the plot represents the three-way interactions between conditions, rational thinking, and avoidance attachments towards a mother figure. According to the visual, conditions significantly interact with rational thinking in predicting women's intention to terminate an abusive relationship only among women with avoidance scores less than -1SD, 1SD to the mean, and the mean to +1SD. At the high level of avoidance attachment (i.e., more than 1SD), conditions do not significantly interact with rational thinking in predicting leaving intention. Among the significant avoidance attachment regions, the treatment condition significantly predicted leaving intention more than the control condition at the rational thinking level close to 4. 
 

Path diagrams {.storyboard}
=====

### Plot 1(Draft)

```{r}

data<-rio::import(here::here("Bigdata.sav"))
```


```{r, results ='hide'}
as.factor(data$Condition)
data$TIM<-data$Condition
data$Int<-data$In_End
data$Avoid<-data$Mom_avoidance
```



```{r}
model<-lm(Int~TIM*NFC*Avoid, data = data)
#issue-cant add label here lbls<-c("Condition", "NFC", "Avoidance", "Intention")

semPaths(model, "std", residuals =FALSE, sizeMan =  8, edge.label.cex = 1, intercepts = FALSE, nCharNodes = 10, theme = "colorblind", pastel = TRUE)




#title = "Three-ways interaction of TIM, NFC, and avoidance")#issue edge.label.cex overlaps)
```





Visualization (3 ways){.storyboard}
======

### Condition x NFC x Avoidance(mother) 

```{r}

data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
Plot1data <- data %>% select("Mom_avoidance", "NFC", "Condition", "In_End")

```



```{r}
Plot1data<-na.omit(Plot1data)
```


```{r}
 
Plot1data$Mom_avoidance <- cut(Plot1data$Mom_avoidance, breaks=c(1, 1.8, 2.72, 3.63, 5), include.lowest= TRUE)
```




```{r}
Plot1data$Condition <- factor(Plot1data$Condition,
levels = c(0,1),
labels = c("Control" , "Treatment"))
```


```{r}

Plot1data$Mom_avoidance <- factor(Plot1data$Mom_avoidance,
levels = c("[1,1.8]"   ,  "(1.8,2.72]"  ,"(2.72,3.63]" ,"(3.63,5]" ),
labels = c("Less than -1 SD", "-1SD to mean", "Mean to + 1SD", "More than+ 1SD"))




```


```{r, fig.width=6}
txt_data <- data.frame(
  NFC = rep(3.99, 4),
  In_End = rep(4.5, 4),
  txt = c(rep("Sig", 3), ""),
  Mom_avoidance = levels(Plot1data$Mom_avoidance)
)

ggplot(Plot1data, aes(x  = NFC, y = In_End, color = Condition))+
  geom_point(alpha = 0.4, position = "jitter")+
  geom_smooth(method = "lm", se  = FALSE)+
  facet_wrap(~Mom_avoidance, scales = "free")+
  scale_y_continuous(limits = c(1,5))+
  scale_x_continuous(limits = c(1,5))+
   scale_color_manual(values = c("#E1BE6A", "#40B0A6"))+
  theme_minimal()+
  geom_text(aes(x = NFC, y = In_End, label = txt),
            hjust = 0,
            data = txt_data,
            inherit.aes = FALSE) +
  labs(x =  "Rational thinking", 
       y = "Leaving intention",  
       title = "The interaction effects of conditions, avoidance attachment, and \n thinking pattern on leaving intention", 
       subtitle = "Avoidance attachment scores towards a mother figure")+
  theme(text = element_text(family = "Calibri"), plot.title = element_text(face = "bold", hjust = 0.5, size = 12, color = "#26734d"))+
   geom_vline(data = filter(Plot1data, Mom_avoidance == "Less than -1 SD"), aes(xintercept = 3.93), color = "black", linetype = "dotted")+
  geom_vline(data = filter(Plot1data, Mom_avoidance == "-1SD to mean"), aes(xintercept = 3.93), color = "black", linetype = "dotted")+
   geom_vline(data = filter(Plot1data, Mom_avoidance == "Mean to + 1SD"), aes(xintercept = 3.93), color = "black", linetype = "dotted")
```


Visualization (2 way){.storyboard}
======

### Adverse childhood experience


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <-factor(data$Condition, 
                        levels = c(0,1),
                        labels = c("Control", "Treatment"))

```


```{r}

p<-ggplot(data, aes(x = ACE, y = Trauma_Knowledge, color = Condition))+
  geom_point(position = "jitter", alpha = 0.4)+
  geom_smooth(method = "lm", se = FALSE)+
   labs (x = "Adverse childhood experience", y = "Trauma knowledge")+
    transition_states(Condition, 
                      transition_length = 2,
                      state_length = 1)+
    enter_fade()+
    enter_grow()+
    exit_fade()+
    exit_shrink()+
    ease_aes()+
    ggtitle("The relationship between adverse childhoode experience \n and trauma knowledge for the {closest_state} condition")+
       theme_minimal()+
  theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(face = 'bold', hjust = 0.5))

  
animate(p)
  
```

### Fear


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```



```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r}
data$Fear<-factor(data$Fear,
                  levels=c(1,2,3,4,5,6), 
                  labels=c("1", "2", "3", "4", "5", "6"))
```



```{r}
ggplot(data, aes(Trauma_Knowledge, Fear, fill = Condition))+
  geom_density_ridges(alpha = 0.5)+
  scale_fill_manual(values = c("#f7786b", "#80ced6"))+
  scale_x_continuous(limits = c(1,5))+
  theme_minimal()+
  theme(text = element_text(family = "Calibri"), plot.title = element_text(hjust = 0.5, size = 10))+
  labs(x = "Trauma Knowledge", title = "Trauma knowledge across the number of fear aspects \n towards a partner and experimental conditions")
##issue cant install ikaebito and the ninja packages for ppt.and also NA
```


### BPD



```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data$Condition <- factor(data$Condition, 
                         levels =c(0,1), 
                         labels = c("Control", "Treatment"))
```


```{r, eval = FALSE}
p<-ggplot(data, aes(BPD, Trauma_Knowledge, color = Condition))+
  geom_density2d(bins = 5, contour_var = "ndensity")+
  geom_point(position = "jitter")+
   scale_color_manual(values = c("#DD517F", "#E68E36"))+
  labs(x = "Borderline personality traits", y = "Trauma knowledge")+
  theme(text = element_text(size = 12, family = "Calibri"),
  plot.title = element_text(face = 'bold'))+
  transition_states(Condition, 
                      transition_length = 2,
                      state_length = 1)+
    enter_fade()+
    enter_grow()+
    exit_fade()+
    exit_shrink()+
    ease_aes()+
    ggtitle("The relationship between borderline personality disorder \n and trauma knowledge for the {closest_state} condition")+
       theme_minimal()+
    theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(face = 'bold', hjust = 0.5))

#issue want to change the color of the title to match with the condition 
  
animate(p)
```



```{r}
#Try
p<-ggplot(data, aes(BPD, Trauma_Knowledge, color = Condition))+
 
  geom_density_2d_filled(alpha = 0.25)+
  geom_point(position = "jitter")+
   scale_color_manual(values = c("#DD517F", "#E68E36"))+
  labs(x = "Borderline personality traits", y = "Trauma knowledge")+
  theme(text = element_text(size = 12, family = "Calibri"),
  plot.title = element_text(face = 'bold'))+
  transition_states(Condition, 
                      transition_length = 2,
                      state_length = 1)+
    enter_fade()+
    enter_grow()+
    exit_fade()+
    exit_shrink()+
    ease_aes()+
    ggtitle("The relationship between borderline personality disorder \n and trauma knowledge for the {closest_state} condition")+
       theme_minimal()+
    theme(text = element_text(size = 12, family = "Calibri"), plot.title = element_text(face = 'bold', hjust = 0.5))

#issue want to change the color of the title to match with the condition and also not so sure about the interpretation of geom_dense 
  
animate(p)
```

---
Some comment about the plot 


Descriptive statistics {.storyboard}
======


```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

### Density of BPD and ACE

```{r}
ggplot(data, aes(ACE, BPD))+
  stat_density2d(geom = "tile", aes(fill = ..density..), contour = FALSE)+
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5), text = element_text(family = "Calibri"))+
  labs(x = "Adverse childhood experience", y = "Borderline personality traits", title = "Density of childhood trauma and borderline personality traits among participants")+
  scale_fill_viridis_c("Density")
```

### Boxplot education across conditions

```{r}
data<-rio::import(here::here("Bigdata.sav"))
```


```{r}
data$Condition<-factor(data$Condition, 
                       levels = c(0,1),
                       labels = c("Control", "Treatment"))
```

```{r}
data$Demo_Edu<-factor(data$Demo_Edu, 
                      levels = c(1, 2,3,4,5,6),
                      labels = c("Less than 8th grade", "High school graduate", "Bachelor's", "Master's", "Doctorate", "Professional school"))
```


```{r}
Edu_count <- data %>% group_by(Condition) %>% count(Demo_Edu)


eduplot<-ggplot(drop_na(Edu_count), aes(x = Demo_Edu, y = n))+
  geom_col(aes(fill = Condition),
                 position = "dodge")



```


```{r}
data$Demo_Age<-factor(data$Demo_Age, 
                      levels = c(1, 2,3,4,5,6),
                      labels = c("18-24", "25-34", "35-44", "45-54", "55-60", "More than 60"))
```



```{r}
Age_count <- data %>% group_by(Condition) %>% count(Demo_Age)


ageplot<-ggplot(drop_na(Age_count), aes(x = Demo_Age, y = n))+
  geom_col(aes(fill = Condition),
                 position = "dodge")



```


```{r}
panel_plot<-plot_grid(ageplot, eduplot, labels = c("A", "B"), ncol =2, nrow =1)
```

```{r}
panel_plot
```

### Correlations

```{r}
data<-rio::import(here::here("Bigdata.sav"))
```

```{r}
data<-data %>% select(Condition, ACE, BPD, Fear, Mom_avoidance, Mom_anxiety, Dad_avoidance, Dad_anxiety, NFC, FI, DVS_state, Trauma_Knowledge, Empowerment_Tradeoffs, Empowerment_InternalTools, Empowerment_ExpectationSupport, DVS_state, )
```


```{r}
colnames(data)<-c("Condition", "ACE", "BPD", "Fear", "Avoidance(mother)", "Anxiety (mother)", "Avoidance(father)", "Anxiety (father)", "NFC", "FI", "Self-efficacy", "Knowledge", "Self-tools", "Tradeoffs", "Support")
```



```{r}
data<-na.omit(data)
```



```{r}
data_cor<-rcorr(as.matrix(data))
```


```{r, results='hide'}
#check correlations
data.frame(data_cor$r) %>% head() %>% kable()
```

```{r, results='hide'}
# p values
data.frame(data_cor$P) %>% head() %>% kable()
```


```{r, results='hide'}
#n
data.frame(data_cor$n) %>% head() %>% kable()
```


```{r}
cors <- function(df) {
   M <- Hmisc::rcorr(as.matrix(df))
   Mdf <- map(M, ~data.frame(.x))
  }
```


```{r, results='hide'}
cors(data) %>% first() %>% head %>% kable()
```


```{r, results='hide'}
cors(data) %>% 
  map(~rownames_to_column(.x, var = "measure1")) %>% 
  map(~pivot_longer(.x, -measure1, "measure2")) %>% 
  bind_rows(.id = "id") %>% 
  pivot_wider(names_from = id,  values_from = value) %>% 
  rename(p = P) %>% 
  mutate(sig_p = ifelse(p < .05,T, F),
         p_if_sig = ifelse(sig_p, p, NA), 
         r_if_sig = ifelse(sig_p, r, NA)) %>% 
  head() %>% 
  kable()
```


```{r, results='hide'}
#Turned format correlations to a function 
formatted_cors<-function(df){
  cors(df)%>%
    map(~rownames_to_column(.x, var="measure1")) %>%
    map(~pivot_longer(.x, -measure1, "measure2")) %>%
    bind_rows(.id = "id") %>%
    pivot_wider(names_from = id, values_from = value) %>%
    rename(p = P) %>%
    mutate(sig_p = ifelse(p < .05, T, F),
           p_if_sig = ifelse(sig_p, p, NA),
           r_if_sig = ifelse(sig_p, r, NA)) 
}

```


```{r, results = 'hide'}
formatted_cors(data) %>% head() %>% kable()
```




```{r, eval = FALSE}
#Plotting 
formatted_cors(data) %>% 
  ggplot(aes(x = measure1, y = measure2, fill = r))+
  geom_tile()+
  labs(x = NULL, y = NULL, fill = "Pearson's \n correlations", title = "Correlations of key variables", subtitle = "Only significant correlations (*p < .05*) are displayed in numbers")+
  scale_fill_viridis_c()+
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0),labels = c("Condition", "ACE", "BPD", "Fear", "Avoidance(mother)", "Anxiety (mother)", "Avoidance(father)", "Anxiety (father)", "NFC", "FI", "Self-efficacy", "Knowledge", "Self-tools", "Tradeoffs", "Support")) +
  theme(text=element_text(family="Calibri"), plot.title = element_text(face = 'bold', hjust = 0.5))
```



```{r, fig.height=10, fig.width=15}
#add significant correlations in table 
##issue should I remove condition?

formatted_cors(data) %>%
  ggplot(aes(measure1, measure2, fill=r, label=round(r_if_sig,2))) +
  geom_tile() +
  labs(x = NULL, y = NULL, fill = "Pearson's\nCorrelation", title="Correlations of key variables",
       subtitle="Only significant Pearson's correlation coefficients shown") +
  scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
  geom_text() +
  theme_classic() +
  scale_x_discrete(expand=c(0,0), labels = c("Condition", "ACE", "BPD", "Fear", "Avoidance(mother)", "Anxiety (mother)", "Avoidance(father)", "Anxiety (father)", "NFC", "FI", "Self-efficacy", "Knowledge", "Self-tools", "Tradeoffs", "Support")) +
  scale_y_discrete(expand=c(0,0), labels = c("Condition", "ACE", "BPD", "Fear", "Avoidance(mother)", "Anxiety (mother)", "Avoidance(father)", "Anxiety (father)", "NFC", "FI", "Self-efficacy", "Knowledge", "Self-tools", "Tradeoffs", "Support")) +
  theme(text=element_text(family="Calibri", size = 12), plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, vjust = 0.70))
```


